---
title: "Unit 4 - 6 Review Starter"
author: "Group 5 - Keneni"
date: "11/1/21"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
library(janitor)
```

## Exercises

# Part I - Data Types and Classes

## Exercise 1 - Create some vectors

```{r month-name-vector}
month_name <- c("January", 
                "February",
                "March",
                "April",
                "May",
                "June",
                "July",
                "August",
                "September",
                "October",
                "November",
                "December")
```

#### Member 1

```{r temperature-vector}
temperature_f <- c(30, 35, 40, 50, 60, 70, 80, 90, 80, 70, 50, 40)
```

#### Member 2

Add your code here.

#### Member 3

```{r create-order-vector}
order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)
```

#### Member 4

```{r nba-season}

nba_season <- c(TRUE, FALSE, T, 0, "TRUE", FALSE, TRUE, FALSE, TRUE, FALSE, FALSE, TRUE)

```

#### Member 5

Add your code here.

## Exercise 2 - Combine into a data frame

```{r merge-two-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 3 - Try plotting with `month_name` on the x axis, then recode factors

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 4 - Join all the data frames, filter randomly, and over-write vector

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 5 - Try to recombine as a data frame, instead use list

```{r try-merge-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.
