---
title: "Unit 4 - 6 Review Starter"
author: "Group 5 - Keneni"
date: "11/1/21"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
library(janitor)
```

## Exercises

# Part I - Data Types and Classes

## Exercise 1 - Create some vectors

```{r month-name-vector}
month_name <- c("January", 
                "February",
                "March",
                "April",
                "May",
                "June",
                "July",
                "August",
                "September",
                "October",
                "November",
                "December")
```

#### Member 1

```{r temperature-vector}
temperature_f <- c(30, 35, 40, 50, 60, 70, 80, 90, 80, 70, 50, 40)
```

#### Member 2

```{r seasons}
season <- c("winter","winter", "spring", "sping", "spring", "summer", "summer", "summer", "fall", "fall", "fall", "winter")

```


#### Member 3

```{r create-order-vector}
order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)
```

#### Member 4

```{r nba-season}

nba_season <- c(TRUE, FALSE, T, 0, "TRUE", FALSE, TRUE, FALSE, TRUE, FALSE, FALSE, TRUE)

```

#### Member 5

Add your code here.

## Exercise 2 - Combine into a data frame

```{r merge-two-vectors, eval = T}
month_order <- tibble::tibble(
  "month_name" = month_name,
  "month_order" = order
)
```

#### Member 1

```{r temperature, eval = T}
temperature <- tibble::tibble(
  "month_name" = month_name,
  "temperature" = temperature_f
)
```
#### Member 2

```{r merge-season-month}
month_season <- tibble::tibble(
  "month_name" = month_name,
  "season" = season
)
```


#### Member 3

```{r merge-two-vectors3}
month_order <- tibble::tibble(
  "month_name" = month_name,
  "month_order" = order
)
```

#### Member 4

```{r merge-nba-season, eval = T}
nba_season <- tibble::tibble(
  "month_name" = month_name,
  "nba_season" = nba_season
)
```

#### Member 5

Add your code here.

## Exercise 3 - Try plotting with `month_name` on the x axis, then recode factors

#### Member 1

```{r allison-ex3}
ggplot(temperature, aes(x = month_name, y = temperature)) +
  geom_point()
```

The plot has the months in alphabetical order on the x-axis instead of their chronological order.

```{r allison-reorder-ex3}
temperature %>%
  mutate(month_name = fct_relevel(month_name, "January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December")) %>%
  ggplot(mapping = aes(x = month_name, y = temperature)) +
  geom_point()
```

Reordering the levels did fix the problem.

#### Member 2

```{r making-ggplot-ju}
ggplot(mapping = aes(x= month_name, y= season))+ geom_point()

```

```{r fct-relevel-ju}
temperature %>%
mutate( month_name = fct_relevel(month_name, "January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December")) 



```


#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 4 - Join all the data frames, filter randomly, and over-write vector

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 5 - Try to recombine as a data frame, instead use list

```{r try-merge-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.                